
\section*{Abstract}

System failures resulting from configuration errors 
have become the major causes affecting the availability and
reliability of today's software systems.
While many misconfiguration handling techniques,
\eg, misconfiguration checking, troubleshooting and repair, 
have been proposed, 
offering automatic verification for configuration files -- like
what we did to regular programs -- is still an open problem.
This is because 1) software configurations are typically written in
poorly structured and untyped representations, and 2) 
writing specifications or constraints for configuration 
verification is non-trivial.
This paper presents, \app, the first automatic verification framework for
software configurations.
For a given configuration file,
\app first analyzes a dataset sample of configuration files,
thus generating a well-structured and probabilistically-typed 
intermediate representations.
Then, \app derives rules and constraints by analyzing
the intermediate representations.
The above two steps have formulated a language model.
Finally, the resulting language model can be used
to verify the given configuration file and capable of 
detecting various tricky errors,
including orderings, value correlation, type errors, and entry missing.
%At the heart of \app lies a novel learning engine, 
%which employs a probabilistic type inference strategy and
%defines an intermediate representation for the rule type.
%With this engine, \app learns various type rules (\eg, orderings,
%value relations, type errors, and user defined rules)
%to verify configuration files of interest.
Our \app framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results. For example, we verify real-world misconfiguration 
files and find 95\% errors are detected.}
